Trauma treatment delay

### 2023-12-06 manuscriptlongversion.Rmd
text

Respiratory rate also had the correlation that lower respiratory rate
correlated with lower rates of delayed treatment among the patients.

@@

The biases that might have been present in this study would be selection
bias and misclassification bias. Selection bias I've explained above but
misclassification bias is something that we can't control in this study.
As previously mentioned, the possible existence of an ofi is decided
during the MoM conferences, where they then add it to the database.
However, they might not always be right in their judgement and
misclassify from time to time, leading to patients landing in the wrong
group in the analysis. This bias should not be big enough to have a
significant impact on the results, but should be kept in mind.

Another limitation with this study is that logistical regressions
assumes that the data is binomial, which the data used is not. The
analysis assumes a linear correlation between the dependent variable and
the independent variable, which is best analysed in a normal
distribution.

@@

Discussing the generalisability of this study, we included the all the
trauma patients treated and Karolinska University Hospital and excluded
40.7% of that population based on that they had not been screened for
ofi. Additional patients were excluded because of missing data, but no
distinct groups except the not screened patients were removed. On that
basis, this population should be a general representation of trauma
patients at the equivalent of a level 1 trauma center, making this study
generalisable. This is in line with our aim, as it was to make it
applicable to the whole trauma patient population

Discuss the generalisability (external validity) of the study results

>>>>

Respiratory rate also had the correlation that lower respiratory rate
correlated with lower rates of delayed treatment among the patients. As
the interval is \>10 to \<29 in the triage guideline, both too low and
too high respiratory rate is not desirable[@EHCP2015]. This might have a
similar explanation to ISS and GCS, that bradypnea in a patient might
attract more attention in the hospital and lower the incidence of
delayed treatment. Another possible explanation might be that patients
with tachypnea might receive higher rates of delayed treatment because
they are more severely injured, therefore a higher risk of missing a
possible injury. Another similar study, which focused on ofi generally,
showed the same correlation, although the significance dissapeared in
the adjusted analysis.

@@

Further discussing possible biases, misclassification bias might also be
present in this study, though it is something that we can't control in
this study. As previously mentioned, the possible existence of an ofi is
decided during the MoM conferences, where they then add it to the
database. However, they might not always be right in their judgement and
misclassify from time to time, leading to patients landing in the wrong
group in the analysis. Also, some patients might have been missed even
before reaching the MoM conference. The patients included in the
conference are selected through audit filters and two specialized
nurses, and patients might be missed in this stage. This bias should not
be big enough to have a significant impact on the results, but should be
kept in mind.

Another limitation with this study is that logistical regressions
assumes that the data is binomial, which the data used is not. The
analysis assumes a linear correlation between the dependent variable and
the independent variable, which is best analysed in a normal
distribution. However, Fischers test showed an association between 4 of
the 7 variables, all of them being the ones who showed an increased or
decreased risk of delayed treatment, showing that these results still
are significant.

@@

Discussing the generalisability of this study, we included the all the
trauma patients treated and Karolinska University Hospital and excluded
40.7% of that population based on that they had not been screened for
ofi. Additional patients were excluded because of missing data, but no
distinct groups except the not screened patients were removed. On that
basis, this population should be a general representation of trauma
patients at the equivalent of a level 1 trauma center, making this study
generalisable. This is in line with our aim, as it was to make it
applicable to the whole trauma patient population. However, as it is a
single center study, where it's result only illustrates the situation in
Stockholm, it is less applicable nationally or globally. This does not
make it only applicable to the population of Stockholm, but is something
to keep in mind.
